\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[sfdefault]{roboto}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
\vspace{2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingList}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}
\linespread{0.95}

\begin{center}
  \textbf{\Huge Aswin V M} \\
  \textsc{Data Analyst \quad - \quad Python Developer \quad - \quad ML Enthusiast} 
  \\[0.5ex]
  \faMapMarker\ Bengaluru, India \quad
  % \small +91-9961044944 $|$ \href{mailto:aswnvm@gmail.com}{aswnvm@gmail.com} $|$
  % \href{https://linkedin.com/in/aswin-vm}{linkedin.com/in/aswin-vm} $|$
  % \href{https://github.com/aswnvm}{github.com/aswnvm} $|$
  % \href{https://aswnvm.space}{aswnvm.space}
\end{center}

\section*{Professional Summary}
Data Analyst with a foundation in Python, SQL, and data visualization. Experienced in building dashboards, deploying machine learning models, automating data workflows, and performing time series forecasting. Skilled in translating datasets into actionable insights, data storytelling, and collaborating cross-functionally to deliver impactful analytical solutions.

\section{Technical Skills}
\resumeSubHeadingList
\resumeItem{\textbf{Languages}: Python, SQL, Shell Scripting}
\resumeItem{\textbf{Data \& ML}: Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn, OpenCV, Time Series Forecasting}
\resumeItem{\textbf{Visualization}: Power BI, Tableau, Advanced Excel (Pivot Tables, Power Query, VLOOKUP)}
\resumeItem{\textbf{Cloud \& Tools}: AWS (S3, EC2, Redshift), Docker, Git, Jira, Jenkins}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingList

\resumeSubheading
{Software Development Engineer (SDE)}{Jan 2023 -- Apr 2025}
{Neuome Technologies}{Bengaluru, India}
\resumeSubHeadingList
\resumeItem{\textbullet\ Built data pipelines for biomedical image analysis and decision support.}
\resumeItem{\textbullet\ Automated anomaly detection, improving data accuracy by 30\%.}
\resumeItem{\textbullet\ Delivered weekly insights to cross-functional stakeholders using visual dashboards.}
% \resumeItem{Designed time-series-based analysis models to improve trend detection and monitoring.}
\resumeSubHeadingListEnd

\resumeSubheading
{Junior Data Analyst}{May 2022 -- Dec 2022}
{Nelise Freelancers}{Thrissur, India}
\resumeSubHeadingList
\resumeItem{\textbullet\ Analyzed recruitment data to identify bottlenecks and forecast hiring trends.}
\resumeItem{\textbullet\ Created Power BI dashboards, reducing hiring time by 25\%.}
\resumeItem{\textbullet\ Collaborated with hiring teams to develop data-driven workflows and visual reporting tools.}
\resumeSubHeadingListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingList
\resumeItem{\textbf{NeuImager} – Gel Imaging Tool (Python, Docker): Built GUI for real-time image capture and lab automation using Python and Docker.}
\resumeItem{\textbf{Truheart} – Cardiac Arrest Detection (Python, AWS, OpenCV): Developed image-based ML system to predict cardiac risks with 93\% accuracy. Integrated real-time detection with AWS cloud storage for alerts and reporting.}
\resumeItem{\textbf{Job Market Analytics} (Python, Power BI, SQL): Designed predictive models and dashboards for HR analytics. Incorporated A/B testing features and campaign success forecasting.}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingList
\resumeSubheading
{B.Tech in Computer Science}{Aug 2017 -- Jun 2021}
{APJ Abdul Kalam Technological University}{Ernakulam, India} 
% \textbf{(CGPA: 6.6/10)}
\resumeSubHeadingListEnd

\section{Certifications}
\begin{tabularx}{\textwidth}{X X}
\textbullet\ Google Data Analytics (Coursera) & \textbullet\ Python for Data Science Bootcamp (Udemy) \\
\textbullet\ Machine Learning I (Columbia University) & \textbullet\ Complete Python Developer – Zero to Mastery (Udemy) \\
% \textbullet\ Power BI for Beginners (Simplilearn)
\end{tabularx}


\section*{Links}
{\small
\begin{center}
\faPhone\ \texttt{+91-9961044944} \hspace{2em}
\faEnvelope\ \href{mailto:aswnvm@gmail.com}{\texttt{aswnvm@gmail.com}} \hspace{2em}
\faGlobe\ \href{https://aswnvm.space}{\texttt{aswnvm.space}} \hspace{2em}
\faLinkedin\ \href{https://linkedin.com/in/aswin-vm}{\texttt{linkedin.com/in/aswin-vm}} \hspace{2em}
\faGithub\ \href{https://github.com/aswnvm}{\texttt{github.com/aswnvm}}
\end{center}
}

\end{document}
